Milestone 2: Hyperparameter Tuning - Nearest Neighbors, Logit w/Linear Propensity Score

### 2019-11-06 perf_release_criteria/milestone_3/feature_selection/feature_selection_nn_mahalanobis.Rmd

@@

```{r boruta_import}
file_name = 'feature_selection_boruta_initial_20191023.RData'
image_file_path = file.path('data', file_name)

>>>>

```{r setup, include=FALSE, echo=FALSE}
require("knitr")
knitr::opts_knit$set(root.dir = dirname(getwd()))
```

@@

```{r boruta_import, echo=FALSE}
file_name = 'feature_selection_boruta_initial_20191023.RData'
image_file_path = file.path('data', file_name)

### 2019-11-06 perf_release_criteria/milestone_3/hyperparameter_tuning/hyperparameter_tuning_nn_logit_linear.Rmd

---
title: "Milestone 2: Hyperparameter Tuning - Nearest Neighbors, GAM Logit"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

This analysis determines the optimal [hyperparameters] (https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.yqukkyb8q4xw) to utilize for computationally intensive statistical matching algorithms proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).

**Matching Algorithm Tested**: Nearest-neighbors with GAM logit distance metric.

@@

results_file_name <- 'hyperparameter_tuning_nn_gam_logit.RData' 
results_file_path <- file.path('data', results_file_name)
```

# Features
The optimal feature set was found in `feature_selection_nn_gam_logit.Rmd`. At the time of this run they were:

@@

```{r fs1, error=TRUE}
fs1_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs1, size=NULL, workers = 64, hps_grid = hps_grid, 
                                       distance = 'GAMlogit', add_interactions=TRUE)

@@

```{r hp_fine}
hps_fine <- list(
  replace = c(TRUE, FALSE),
  caliper = seq(0.5, 1.3, by=0.2),
  calclosest = c(TRUE, FALSE),
  ratio = c(1, 2, 3)
)

@@

fs1_results_final <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs1, size=NULL, workers = 64, hps_grid = hps_fine_grid, 
                                       distance = 'GAMlogit', add_interactions=TRUE)
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)

@@

```{r fs5, error=TRUE}
fs5_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs5, size=NULL, workers = 64, hps_grid = hps_grid, 
                                       distance = 'GAMlogit', add_interactions=FALSE)

fs5_results_df <- fs5_results %>% bind_rows()
fs5_results_df %>% group_by_at(setdiff(names(fs5_results_df), "scores")) %>% 
  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs5_results_df
knitr::kable(fs5_results_df[order(fs5_results_df$mean), ])
```

# Push to GCP
Save the resultant dataset and bootstrap samples to an R image.

>>>>

---
title: "Milestone 2: Hyperparameter Tuning - Nearest Neighbors, Logit w/Linear Propensity Score"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

This analysis determines the optimal [hyperparameters](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.yqukkyb8q4xw) to utilize for computationally intensive statistical matching algorithms proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).

**Matching Algorithm Tested**: Nearest-neighbors with logit distance metric transformed back to linear scale.

@@

results_file_name <- 'hyperparameter_tuning_nn_logit_linear.RData' 
results_file_path <- file.path('data', results_file_name)
```

# Features
The optimal feature set was found in `feature_selection_nn_logit_linear.Rmd`. At the time of this run they were:

@@

```{r fs1, error=TRUE}
fs1_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs1, size=NULL, workers = 64, hps_grid = hps_grid, 
                                       distance = 'linear.logit', add_interactions=TRUE)

@@

```{r hp_fine}
hps_fine <- list(
  replace = c(TRUE, FALSE),
  caliper = seq(0.2, 0.8, by=0.2),
  calclosest = c(TRUE, FALSE),
  ratio = c(1, 2, 3)
)

@@

fs1_results_final <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs1, size=NULL, workers = 64, hps_grid = hps_fine_grid, 
                                       distance = 'linear.logit', add_interactions=TRUE)
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)

@@

```{r fs5, error=TRUE}
fs3_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_8x']], fs5, size=NULL, workers = 64, hps_grid = hps_grid, 
                                       distance = 'linear.logit', add_interactions=FALSE)
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)

fs3_results_df <- fs3_results %>% bind_rows()
fs3_results_df %>% group_by_at(setdiff(names(fs3_results_df), "scores")) %>% 
  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs3_results_df
knitr::kable(fs3_results_df[order(fs3_results_df$mean), ] %>% head(20))
```

# Serialize and Push to GCP
Save the resultant dataset and bootstrap samples to an R image.
